% Rajat Shukla's Resume
% Created: 05 Dec 2014
% Last Modified: 11 Nov 2015

\documentclass[a4paper,11pt,oneside]{article}
\usepackage[a4paper]{geometry}
\usepackage{tgpagella}

\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{RAJAT SHUKLA}
\newcommand{\addr}{BTM Layout, Bengaluru KA - 560076}
\newcommand{\contact}{shk.rajat@gmail.com | +91 7406152642}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
  \begin{center}\fontfamily{phv}\selectfont\LARGE#1\end{center}
}

% This defines how the name looks
\newcommand{\bignamenew}[1]{
  \begin{center}\selectfont\Huge#1\end{center}
}

% This defines how the address information will look
\newcommand{\addrinfo}[1]{
  \begin{center}\selectfont\small\textit#1\end{center}
}

% This defines how the contact information will look
\newcommand{\contactinfo}[1]{
  \begin{center}\selectfont\small\textbf#1\end{center}
}

\newcommand{\resdescpara}[1]{
  \vspace{-5pt}
\item
  #1
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
  \vspace{4pt}
         {\fontfamily{phv}\selectfont\Large#1}
         \begin{itemize}
           \vspace{3pt}
}{
         \end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
  \vspace{-4pt}
\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
  \vspace{-1pt}
\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
  \vspace{-5pt}
\item
  \textbf{#1} --- #2 \\
  \textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
  \resbigitem{#1}{#2}{#3}
  \vspace{-2pt}
  \begin{itemize}
}{
  \end{itemize}
}

% This is a list that comes without a resbigitem
\newenvironment{ressubsecwo}[3]{
  \resbigitem{#1}{#2}{#3}
  \vspace{0pt}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
  \resitem{\textbf{#1}}
  \vspace{-5pt}
  \begin{itemize}
}{
  \end{itemize}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name

%\bignamenew{\name}
\bigname{\name}

% Addr
\vspace{2 pt}
\addrinfo{\addr}

% Contact
\contactinfo{\contact}
\vspace{8 pt}

%%%%%%%%%%%%%%%%%%%%%%%%
% Objective:

\begin{ressection}{Objective}
%  \resitem{
%    I am looking for a switch to work in backend developement as
%    I have more developement experience than core 'DevOps' experience.
%  }
  \resitem{
    I have worked extensively on infra automation (treating
    Infrastructure as Code).
  }
  \resitem{
    Experienced with AWS technologies, ELK stack, microservices, etc.
  }
\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
% Summary:

\begin{ressection}{Summary}
  \resitem{
    Senior Software Engineer with almost 5 years of experience.
  }
  \resitem{
    Working on writing backend software and automating infra.
  }
  \resitem{
    Knowledge of AWS technologies, ELK, Nagios, Graphite, etc.
  }
  \resitem{
    Knowledge of backend software development.
  }
  \resitem{
    Have previously worked on Android, iOS development.
  }
\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
% Education:

% \begin{ressection}{Education}
%   % GB Pant
%   \begin{ressubsec}{G.B. Pant Engineering College}{Pauri, Uttarakhand}{B.Tech in Computer Science and Engineering: June 2013}
%     \ressubitem{Score : 69.96\% (overall)}
%   \end{ressubsec}
%   % XII
%   \ressubsecwo{AISSCE, Standard XII}{CBSE, Delhi}{Score : 83.20\% (overall): June 2009}
%   % X
%   \ressubsecwo{AISSE, Standard X}{CBSE, Delhi}{Score : 87.20\% (overall): June 2007}
%   % END
% \end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
% Work experience

\begin{ressection}{Experience}
  % Webyog
  \begin{ressubsec}{NewtonHQ.com - CloudMagic}{Bengaluru, KA}{Software Engineer: Aug, 2014--present}
    \ressubitem{
      Working in the backend team automating infra setup
      and deployment using our own provisioning and deployment software.
    }
    \ressubitem{
      Setup and maintenance of federated graphite and
      clustered elasticsearch (ELK) and PHP wrapper over their APIs.
    }
    \ressubitem{
      Automated recovery of both stateless/stateful EC2 instances whenever they are marked
      system/instance impaired by AWS or have a scheduled event pending.
    }
    \ressubitem{
      Wrote a wrapper over Route53 API to enable us to use DNS like a load
      balancer reducing costs in test environments.
    }
    \ressubitem{
      Wrote monitoring using graphite APIs and Cloudwatch
      APIs that monitors performance of our EC2 instances, RDS, redis,
      etc.
    }
    \ressubitem{
      Automatic autoscaling of EC2 instances based on
      parameters like Gearman Job count, SQS incoming messages,
      ELB request count, CPU Usage, etc.
    }
    \ressubitem{
      Automated creation/termination, stop/start/refresh of a full Newton
      test environment, reducing the time and effort spent otherwise.
    }
    \ressubitem{
      Automated syncing logs from instances to a single
      instance (using rsync) and then archiving them
      to S3 for long term storage.
    }
    \ressubitem{
      Have worked on Nagios for monitoring, Twilio and Pagerduty for
      call alerts.
    }
    \ressubitem{
      Technologies - AWS PHP SDK, Python, PHP, Capistrano,
      ElasticSearch, Graphite, etc.
    }
  \end{ressubsec}
  % Xora
  \begin{ressubsec}{Xora, a ClickSoftware company}{Bengaluru, KA}{Software Engineer: Sept, 2013--Aug, 2014}
    \ressubitem{
      Worked on Xora StreetSmart, on various mobile platforms, such as
      Android, Blackberry, MIDP and Brew.
    }
    \ressubitem{
      Worked on implementing Trips feature in the app, wherein it had
      to collect breadcrumb trail of a user and calculate distance and
      fuel usage.
    }
    \ressubitem{
      Helped QA team implement testing using automation testing framework Calabash.
    }
    \ressubitem{
      Technologies - Android SDK, Blackberry SDK, Java ME, Brew SDK.
    }
  \end{ressubsec}
  % Xamii
  % \begin{ressubsec}{Xamii, an examination solution}{Side project}{March, 2016--present}
  %  \ressubitem{A solo project by me, to facilitate online examinations, still under construction.}
  %  \ressubitem{It will provide a complete solution to hanlde e-examinations.}
  %  \ressubitem{Technologies - Python, Mysql, Nginx, etc.}
  % \end{ressubsec}
  % GB Pant
  %\begin{ressubsec}{G.B. Pant Engineering College}{Pauri, UK}{Final year project: 2013}
  %  \ressubitem{Designed a prototype for cluster computation, using the Master-Slave model.}
  %  \ressubitem{Simulated parallel execution of algorithms such as -- Prime Sieve Algorithm, Matrix Chain Multiplication Algorithm, Quick Sort Algorithm.}
  %  \ressubitem{Developed programs based on famous LCG algorithm and Mersenne Twister algorithm to feed random numbers.}
  %\end{ressubsec}
  % Github
  \begin{ressubsec}{Repositories on github.com}{rajats105}{https://github.com/rajats105}
    \ressubitem{
      arana: Web scaper built on top of a headless web browser
      PhantomJS, and it can scrape Single Page Applications easily.
    }
    \ressubitem{
      prezto: ZSH config framework forked from sorin-ionescu/prezto.
      I added customizations to support conda, rvm, etc and added my
      theme - electro.
    }
    \ressubitem{
      prelude: Emacs configuration framework forked from
      bbatsov/prelude, with my own customizations on top of it.
    }
    \ressubitem{
      projecteuler: Collection of programs to solve problems on
      https://projecteuler.net/.
    }
    \ressubitem{
      dotfiles: Collection dotfiles, e.g conky config, .zshrc,
      .Xresources, etc.
    }
  \end{ressubsec}
  % END
\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
% Skills

\begin{ressection}{Skills}
  % Languages
  \begin{reslist}{Languages:}
    \ressubitem{Currently : PHP, Python, JS, SQL and Shell.}
    \ressubitem{Past : C and Java.}
  \end{reslist}
  % Tools
  \begin{reslist}{Software:}
    \ressubitem{Tools : Emacs, Chef, Jenkins, Ansible, etc.}
    \ressubitem{Software : Graphite, Grafana, ELK, Nagios, etc.}
    \ressubitem{Others : AWS SDK, PhantomJS, Kohana, etc.}
  \end{reslist}
  % END
\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
% Achievements

% \begin{ressection}{Achievements and Activities}
%   \resitem{Secured 95.05 percentile (overall) in pH test conducted by eLitmus (Aug 2013).}
%   \resitem{Solved 44 problems on Projecteuler (https://projecteuler.net/profile/rajats105.png).}
%   \resitem{Scored 98 out of 100 marks in exam of mathematics in Class X.}
%   \resitem{Attended Amazon AWS re:invent 2015 conference at Las Vegas.}
% \end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
% Interests

% \begin{ressection}{Hobbies and Interests}
%  \resitem{Programming and technology.}
%  \resitem{Reading.}
%  \resitem{Playing games, e.g. Dota 2, PUBG.}
%  \resitem{Listnening to music.}
% \end{ressection}

\end{document}
% THE END ;)
